%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
% \nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
% \usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
% \setlength{\hintscolumnwidth}{2.3cm}                % if you want to change the width of the column with the dates
% \setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Jacques}{KAISER}
\title{Resumé}                               % optional, remove / comment the line if not wanted
\address{Level 6, 228 Flinders Lane}{Melbourne, Victoria}{Australia 3000}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{0490 159 046}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
% \phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{jacko.kaiser@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.jacqueskaiser.com}                         % optional, remove

\begin{document}


\recipient{Zendesk Recruitment team}{
Level 1, 482 Bourke Street
Melbourne, Victoria 3000,
Australia}
\date{October 23, 2013}
\opening{Dear Zendesk}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}

\makelettertitle

This letter is to express my interest in the JavaScript Developer position posted on seek.

Recently graduated with a Master of Computer Science, I am an enthusiastic developer.

% Amazing Developer :
%% research lab => independance, problem solving, creativity and initiatives
%% Skimlab => startup skills, web, independant
%% MOOC => different way of learning, open minds
Undertaking, I know how to take advantage of surrounding opportunities.
This is demonstrated by all the relevant summer internships I have been involved in.
Working in different environments lying from research laboratory to startup made me become a versatile and independent programmer.

% New to web programming, but quick learner and devoted
Even though I started web programming quite recently, learning it has been a quick process thanks to my initiatives.
Indeed, seduced by the ease to write portable applications, I have spent the last 12 months gathering as many web experiences as possible.
The most important one has been my internship at Skimlab, where I had the opportunity to develop a powerful web application
relying on new technologies and industry best practices.
More details on my experiences are available on \href{http://www.jacqueskaiser.com}{www.jacqueskaiser.com}; and being itself a project, you can browse the source code on \href{https://www.github.com/jackokaiser/chezjacking}{github}.

% I care about high quality code, and people for who I work are satisfied. Look at my references
As you will see from my \href{http://www.au.linkedin.com/pub/jacques-kaiser/28/6a8/231/en}{references} and from my website, if I join your company
you will gain an autonomous, open-minded and very efficient programmer.
From my side, I am eager to improve my proficiency by working in depth with cutting edges technologies.
Moreover being involved in a professional environment is conductive to quick learning of a sound and solid knowledge,
and it is also gratifying to contribute to a real product.

I am very excited to learn more about this opportunity and share how I will be a great fit for Zendesk.

\makeletterclosing


\end{document}
